Co-moving stars in \textsl{Gaia DR1}: a catalog of genuine comoving star pairs from low-resolution spectroscopic follow-up

### 2017-06-02 paper/comoving-followup.tex
omg sky line hacking

We observed a total of 765 unique sources over 5 nights from (UT) 2017-03-11 to
2017-03-15, corresponding to 321 unique star pairs and $\approx 120$ calibration
targets.
The calibration targets have previously measured radial velocities and chemical
abundances, which will be used for validation of our reduction pipeline and in
future work to measure metallicities and stellar parameters for each observed
source using \project{The Cannon} (\citealt{Ness:TODO}).
The spectra were reduced and calibrated using a custom, publicly-available
pipeline written in \python,\footnote{Released along with the code used to
generate the figures in this document at
\url{https://github.com/adrn/GaiaPairsFollowup}.} summarized below.

@@

This wavelength calibration procedure produces a nightly model for the nonlinear
dispersion of wavelength as a function of pixel value for each extracted 1D
spectrum.
However, because of flexure in the spectrograph, each observation will have an
additional, unknown constant offset of, typically, $\approx 0.5$--$2~{\rm \AA}$,
corresponding to a significant velocity offset at ${\rm H}\alpha$ of
$\approx 20$--$100~\kms$.
\figurename~\ref{fig:sample-spectra} shows a random sample of 10 source spectra
of comoving star pair members normalized to 1 at $\lambda = 5500~{\rm \AA}$ and
shifted by index for visualization.
From the appearances of these 10 alone, it seems there is a mix of metallicities
and spectral types.
Note that the spectra are not flux-calibrated, as we only care about measuring
radial velocities from this sample.

>>>>

We observed a total of 765 unique sources over 5 nights from (UT) 2017-03-11 to
2017-03-15, corresponding to 321 unique star pairs and $\approx 120$ calibration
targets.
The calibration targets have previously measured radial velocities and chemical
abundances, which will be used for validation of our reduction pipeline and in
future work to measure metallicities and stellar parameters for each observed
source using \project{The Cannon} (\citealt{Ness:TODO}).
The spectra were reduced and calibrated using a custom, publicly-available
pipeline written in \python,\footnote{Released along with the code used to
generate the figures in this document at
\url{https://github.com/adrn/GaiaPairsFollowup}.} described below.

@@

This wavelength calibration procedure produces a nightly model for the nonlinear
dispersion of wavelength as a function of pixel value for each extracted 1D
spectrum.
However, because of flexure in the spectrograph, each observation will have an
additional, unknown constant offset of, typically, $\approx 0.5$--$2~{\rm \AA}$,
corresponding to a significant velocity offset at ${\rm H}\alpha$ of
$\approx 20$--$100~\kms$.
\figurename~\ref{fig:sample-spectra} shows a random sample of 10 source spectra
of comoving star pair members normalized to 1 at $\lambda = 5500~{\rm \AA}$ and
shifted by index for visualization.
From the appearances of these 10 spectra, it seems there is a mix of
metallicities and spectral types amongst the observed targets.
Note that the spectra are not flux-calibrated, as we only care about measuring
radial velocities from this sample.
